Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-10-07 paper/paper.tex
pass on macros
new edits

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, we found many tests
based on Node.js~\cite{node} that
%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
%\Igor{yes, it is. Some Node internal features are not included in the
%JS engine, including some keywords (ie. require, module).  In
%addiction, a project with nodejs require a package.json with a lot of
%external dependencies.}
require libraries to be installed before running the test and
different tests require different sets of libraries. Supporting those
tests would require an extra setup step and would slow down the
execution of our experiments. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.

\lbrack{}Test Harness\rbrack{}~We noticed that some engines use a
custom shell to run tests, including a harness with specific
assertions. For example, tests provided by Mozilla contain a lot of
custom functions (\eg{}, \CodeIn{assertThrowsInstanceOf},
\CodeIn{assertEqArray}, and \CodeIn{getPromiseResult}) and those are
included in the shell to make the test run correctly.  For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine. For instance, if a test had a statement
such as \texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the
condition returns false.  If we found the change would require
substantial manual work, we opted to discard the test instead.

@@

\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
we discarded duplicate tests with Mozilla and \jsc. The rationale is to
avoid inflating results and giving credit where it is due. We also
wrote a script that compares each pair of tests from different suites
for similarity. We did not find identical tests, although it is
possible there are equivalent tests modulo renaming.

@@

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 330 170 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure
    overview.}
\end{figure}

@@

\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produced. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.5ex} \lbrack{}Non-Exploratory Phase\rbrack{} Results
obtained in the exploratory phase confirmed our expectations that most
of the bugs found during the initial period of investigation were
related to \hi\ warnings. For that reason, we changed our inspection
strategy. This time, some of the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9
    & Timeout/OME & 30 & 15 \\ % 28 & 13
    & * Invalid Input & 46 & 55 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
    & Bug & 15 & 7\\
    \bottomrule
  \end{tabular}
\end{table}

@@

As it is the case of most empirical evaluations, our findings are
subject to internal, external, and construct threats to
validity. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines. To
mitigate this threat, we carefully selected inputs from various
sources according to a well-defined criteria. Likewise, we selected
the engines by using using a documented criteria and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market.  A
reader might argue that since we mined files from other JS engines,
such as Duktape, JerryScript, JSI, and Tiny-js, we could also have ran
test transplantation on them. We decided not to do so for different
reasons: JSI was deprecated, TinyJS is not actively
maintained. Finally, at the time we started this work, Duktape and
JerryScript did not provide support to ES6. We checked this
information again in Jun 2020, and they are still only partially
supporting ES6. In terms of construct validity, we used standard
metrics to determine the effectiveness of the testing techniques we
studied (\eg{}, number of bugs confirmed and fixed and
severity). Engine developers were responsible for determining the
labels of the bug reports and their severity. Consequently, these
metrics originate from a trusted source.

>>>>

\vspace{0.2cm}
\noindent
\textbf{Cleansing}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, we found many tests
based on Node.js~\cite{node} that
%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
%\Igor{yes, it is. Some Node internal features are not included in the
%JS engine, including some keywords (ie. require, module).  In
%addiction, a project with nodejs require a package.json with a lot of
%external dependencies.}
require libraries to be installed before running the test and
different tests require different sets of libraries. Supporting those
tests would require an extra setup step and would slow down the
execution of our experiments. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.

\vspace{0.2cm}
\noindent
\textbf{Test Harness}~We noticed that some engines use a
custom shell to run tests, including a harness with specific
assertions. For example, tests provided by Mozilla contain a lot of
custom functions (\eg{}, \CodeIn{assertThrowsInstanceOf},
\CodeIn{assertEqArray}, and \CodeIn{getPromiseResult}) and those are
included in the shell to make the test run correctly.  For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine. For instance, if a test had a statement
such as \texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the
condition returns false.  If we found the change would require
substantial manual work, we opted to discard the test instead.

@@

\vspace{0.2cm}
\noindent
\textbf{Dedup}~The number of tests in \veight\ is low because
we discarded duplicate tests with Mozilla and \jsc. The rationale is to
avoid inflating results and giving credit where it is due. We also
wrote a script that compares each pair of tests from different suites
for similarity. We did not find identical tests, although it is
possible there are equivalent tests modulo renaming.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.85\textwidth]{figs/diff-testing-runtimes-2.pdf}
  \caption{\label{fig:workflow}The workflow of the referred differential
testing approach.}
\end{figure}

@@

\vspace{0.2cm}
\noindent
\textbf{Exploratory Phase} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produced. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.2cm}
\noindent
\textbf{Non-Exploratory Phase} Results
obtained in the exploratory phase confirmed our expectations that most
of the bugs found during the initial period of investigation were
related to \hi\ warnings. For that reason, we changed our inspection
strategy. This time, some of the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9
    & Timeout/OME & 30 & 15 \\ % 28 & 13
    & * Invalid Input & 46 & 55 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
    & Bug & 16 & 7\\
    \bottomrule
  \end{tabular}
\end{table}

@@

As it is the case of most empirical evaluations, our findings are
subject to internal, external, and construct threats to
validity. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines.
We though carefully selected inputs from various
sources according to a well-defined criteria (Section~\ref{sec:seeds}).
Likewise, we selected
the engines by using using a documented criteria (Section~\ref{sec:methodology:engines})
and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market.  A
reader might argue that since we mined files from other JS engines,
such as Duktape, JerryScript, JSI, and Tiny-js, we could also have ran
test transplantation on them. We decided not to do so for different
reasons: JSI was deprecated, TinyJS is not actively
maintained. Finally, at the time we started this work, Duktape and
JerryScript did not provide support to ES6. We checked this
information again in Jun 2020, and they are still only partially
supporting ES6. In terms of construct validity, we used standard
metrics to determine the effectiveness of the testing techniques we
studied (\eg{}, number of bugs confirmed and fixed and
severity). Engine developers were responsible for determining the
labels of the bug reports and their severity. Consequently, these
metrics originate from a trusted source.
